analyze_bb_fullset

### 2020-01-30 analysis/analysis_bb_fulldataset_2.Rmd
code to start bb analyses in full data, part2

bb_all <- bb_all %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(d$age_day_bin)))
```

bin_size = 6
min_age = 6
max_age = 30
bin_starts = seq(min_age, max_age+1,bin_size)
bins = c(bin_starts)

@@

poses_by_size_by_frame <- bb_all %>%
  filter(label=="pose") %>%
  group_by(vid_name, frame, age_days, child_id) %>%
  summarize(num_poses = sum(label=="pose"), avg_area = mean(area), avg_x = mean(center_x), avg_y = mean(center_y))
# 
# save(hands_by_size_by_frame, file="../data/hands_by_size_by_frame.RData")
# save(faces_by_size_by_frame, file="../data/faces_by_size_by_frame.RData")
# save(poses_by_size_by_frame, file="../data/poses_by_size_by_frame.RData")
```

@@

@@

bb_all <- bb_all %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1)))

poses_by_size_by_frame <- poses_by_size_by_frame %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin)))

@@

```{r}
subset_A <- poses_by_size_by_frame %>%
  filter(child_id == "A") %>%
  filter(age_days < 400)

subset_A <- subset_A %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin)))
```

```{r}
pose_summary_by_age_days <- poses_by_size_by_frame %>%
  group_by(age_days, child_id) %>%
  summarize(num_detect = length(frame), avg_area_age = mean(avg_area), avg_people = mean(num_poses)) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1)))

face_summary_by_age_days <- faces_by_size_by_frame %>%
  group_by(age_days, child_id) %>%
  summarize(num_detect = length(frame), avg_area_age = mean(avg_area), avg_faces = mean(num_faces))

hand_summary_by_age_days <- hands_by_size_by_frame %>%
  group_by(age_days, child_id) %>%
  summarize(num_detect = length(frame), avg_area_age = mean(avg_area), avg_faces = mean(num_hands))

ggplot(pose_summary_by_age_days, aes(x=age_days, y=log(avg_area_age), col=child_id, size=num_detect)) +
  geom_point(alpha=.2) +
  geom_smooth(span=10)

ggplot(face_summary_by_age_days, aes(x=age_days, y=log(avg_area_age), col=child_id, size=num_detect)) +
  geom_point(alpha=.2) +
  geom_smooth(span=10)

ggplot(hand_summary_by_age_days, aes(x=age_days, y=log(avg_area_age), col=child_id, size=num_detect)) +
  geom_point(alpha=.2) +
  geom_smooth() 
```

>>>>

bb_all <- bb_all %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(d$age_day_bin)))
# 
# bin_size = 6
# min_age = 6
# max_age = 30
# bin_starts = seq(min_age, max_age+1,bin_size)
# bins = c(bin_starts)
```

@@

poses_by_size_by_frame <- bb_all %>%
  filter(label=="pose") %>%
  group_by(vid_name, frame, age_days, child_id) %>%
  summarize(num_poses = sum(label=="pose"), avg_area = mean(area), avg_x = mean(center_x), avg_y = mean(center_y))
```

@@

save(hands_by_size_by_frame, file="../data/hands_by_size_by_frame.RData")
save(faces_by_size_by_frame, file="../data/faces_by_size_by_frame.RData")
save(poses_by_size_by_frame, file="../data/poses_by_size_by_frame.RData")

@@

bb_all <- bb_all %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(d$age_day_bin)))

poses_by_size_by_frame <- poses_by_size_by_frame %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(d$age_day_bin)))

@@

```{r}
summary_by_age <- bb_all %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_detect = length(face_openpose), prop_faces = sum(face_openpose) / num_detect,  prop_hands = sum(hand_openpose) / num_detect, face_or_hand = sum(person_openpose)/ num_detect, face_and_hand = sum(both_openpose)/ num_detect)
